%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Preamble
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{article}
%
% Packages and other includes
% Pagination
\usepackage[letterpaper, margin=1in]{geometry}

%
% Graphics, floats, tables
\usepackage{graphicx, xcolor, float, array}
\graphicspath{{image/}}
%
% Fonts
\usepackage[T1]{fontenc} % best for Western European languages
\usepackage{lmodern} % Latin Modern instead of CM
\usepackage{textcomp} % required to get special symbols
%
% Math
\usepackage{amsmath, amssymb}
\usepackage{enumerate}
\usepackage{braket}
% 
% Hyperlinks
\usepackage[colorlinks,linkcolor={red},citecolor={blue},
urlcolor={blue}]{hyperref} 
%
% Definitions and settings
% Paragraph indent and spacing
\setlength{\parskip}{0.4\baselineskip}
\setlength{\parindent}{0in}
%
% Math mode version of "r" column type (requires array package)
\newcolumntype{R}{>{$}r<{$}}
\newcommand{\brian}[1]{{\color{orange}{#1}}}
% Title, authors, date
\title{\textbf{Homework 4}}
\date{\vspace{-2em}\today}

\begin{document}

\maketitle 

Weekly homework assignments are posted approximately one week prior to the
due date. Collaborations are encouraged and students must report all collaborators
in writing on each assignment. All external sources (websites, books) must be
properly cited. Additional problems are listed at the end of each assignment.
This week's assignment is due \textit{Friday, Sept 30thth at 11:59pm.}

\textbf{Molar Mass and Mass Percent Composition}

1) A metal M forms an oxide with the formula M$_2$O$_3$, for which the mass
percentage of the metal is $69.9\%$. (3 pts)

a) What is the identity of the metal?

b) Write the name of the compound.

\vspace{1.65in}

\textbf{Empirical and Molecular Formula}

2) A chemist performed a chemical reaction that combines 7.035g sulfur with
fluorine to produce 23.42g of gas. Report to 4 sig figs. (3 pts)

a) What is the empirical formula of the gas?

b) Assuming that the empirical and molecular formulas of the compound are the same,
what is its name?

\newpage

\textbf{Molarity and Dilution}

3) Medical hospitals often prepare solutions with specific ionic concentrations. A
lab technician makes a 150.0mL solution containing 0.750g NaCl and 0.45g KCl, as well
as glucose and other sugars. What is the concentration of chloride ions in the solution?
Report to 3 sig figs. (2 pts)

\vspace{2in}

4) Explain how to prepare 0.750M Na$_2$CO$_3$ solution by starting with

a) 1.00M Na$_2$CO$_3$ solution,

b) Solid Na$_2$CO$_3$. (2 pts)


\vfill

\textbf{Optional Textbook Problems:} Ch. 4- $4.3-4.7$ odd, $4.21-4.47$ odd, $4.61-4.89$ odd

\end{document}
